All MMs and AMCEs

### 2023-09-09 notebook/results.qmd
Add TODO

>>>>

TODO: Hypotheses

- General basic ones, like only each lever, one at a time
- More specific ones that we preregistered. These conditional ones are tricky because there are so many different possible questions we could explore (at least 576 of them!). To avoid selective p-hacking, we pre-registered a handful that we're most interested in, and we only explore those.
